### 2015-06-16 stochastic/stochastic-recovery.Rmd
save stochastic recovery scrip

@@

```{r}
pdf("poster-beta.pdf", width = 4, height = 4)
plot(beta[upper.tri(beta)], true_beta[upper.tri(beta)],
     pch = 16, cex = .4, col = "#00000020",
     xlab = "Estimated interaction strength",
     ylab = "\"True\" interaction strength",
     main = "Recoverd pairwise interactions",
     las = 1,
     cex.axis = 0.75
    )
text(
  -0.7, 
  1,
  paste(
    "R^2 =", 
    signif(cor(beta[upper.tri(beta)], true_beta[upper.tri(beta)])^2, 2)
  )
)

@@

```{r}
pdf("poster-alpha.pdf", width = 4, height = 4)
plot(alpha_env, true_alpha_env,
     pch = 16, cex = .4, col = "#00000090",
     xlab = "Estimated environmental coefficient",
     ylab = "\"True\" environmental coefficient",
     main = "Recovered environmental coefficients",
     las = 1,
     cex.axis = 0.75
)
text(
  -1, 
  1,
  paste(
    "R^2 =", 
    signif(cor(c(alpha_env), c(true_alpha_env))^2, 2)
  )
)
dev.off()

>>>>

# Estimating pairwise interactions by stochastic maximum likelihood

@@

```{r}
pdf("poster-beta.pdf", width = 4, height = 5)
plot(beta[upper.tri(beta)], true_beta[upper.tri(beta)],
     pch = 16, cex = .4, col = "#00000020",
     xlab = "Estimated interaction strength",
     ylab = "\"True\" interaction strength",
     main = paste0("Recoverd pairwise interactions", "\nN = ", choose(n_spp, 2)),
     las = 1,
     cex.axis = 0.75
    )
text(
  -0.7, 
  1,
  paste(
    "R^2 =", 
    signif(cor(beta[upper.tri(beta)], true_beta[upper.tri(beta)])^2, 2)
  )
)

@@

```{r}
pdf("poster-alpha.pdf", width = 4, height = 5)
plot(alpha_env, true_alpha_env,
     pch = 16, cex = .4, col = "#00000090",
     xlab = "Estimated environmental coefficient",
     ylab = "\"True\" environmental coefficient",
     main = paste0("Recoverd environmental coefficients", "\nN = ", length(alpha_env)),
     las = 1,
     cex.axis = 0.75
)
text(
  -1, 
  1,
  paste(
    "R^2 =", 
    signif(cor(c(alpha_env), c(true_alpha_env))^2, 2)
  )
)
dev.off()
